Git Learning Notes

### 2014-09-11 BackMatter/app_training.tex
training instruction added

A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\textwidth]{CVD_model.jpg}
\caption{Sketch of CVD system for oxide growth, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves. Note: the thermal sensor attached on H-1 is not shown. }
\label{fig:ch2cvd}
\end{figure}

The following text will refer to this diagram using \fbox{symbol in box} when a specific component is mentioned. Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization system, a cold trap is used and oxygen tank is absent; whereas in the ZnTe system, a pressure controller is added and hydrogen instead of oxygen is used.

\section{Basic Operation}
Before performing growth, check the CVD system to confirm its normal state, where the vacuum in idle status is manifested as:
\begin{itemize}
\item 5-7 mTorr reading for the pressure gauge (\fbox{P-1})of ZnTe CVD;
\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
\item 45-50 mTorr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD. 
\end{itemize} 
and the mass flow controller reading (\fbox{MFC}) should be either negative or zero. If large deviation occurs, check the vacuum sealing and report to lab manager.

\subsection{Venting the chamber}
To load/unload sample into/out of the chamber, one first needs to bring the pressure up to 1 atm. This is done by purging the chamber using Ar gas using steps as following (\textbf{FOLLOW THE EXACT ORDER}):
\begin{enumerate}
\item close \fbox{V-5}, one should observe \fbox{P-1} reading increases;
\item toggle Ar gas switch from OFF to ON, wait for 10 s;
\item toggle Ar gas purge switch, watching \fbox{P-1} closely; When the chamber is purged with Ar, the indications of actual pressure reaching 1 atm inside are shown as: 
\begin{itemize}
\item 760 Torr reading for the ZnTe CVD;
\item 32-33 Torr reading for the oxide CVD;
\item 24 Torr reading for the sulfur CVD. 
\end{itemize} \textbf{Avoid} using higher venting pressure. 
\item Turn off Ar purge switch rapidly when 1 atm is reached; 
\item Slowly open \fbox{V-4} to test the ``water'' level in \fbox{B-1}. Close \fbox{V-4} if the level goes up; fully open \fbox{V-4} if otherwise. 
\end{enumerate}
%Using the same procedure when harvesting the samples.

@@

\subsection{Starting heating} 
The heating is controlled by a close-loop PID method, with the control panel shown in Fig.~\ref{fig:omega}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{omega_temp}
\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
\label{fig:omega}
\end{figure}

Change to heating mode by the following steps:
\begin{enumerate}
\item turn on the voltage transformer; 
\item hold $\Xi$ key for 3 second;
\item use $\nabla$ or $\Delta$ key to circle until ``r.s'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

@@

\section{Emergence Procedures}

@@

@@

The substrate treatment in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;  
\item Load a thin layer of 3N W powder on the clean substrate, spread them uniformly by putting the polished side of another clean Si substrate against the power and sliding the top substrate gently; 
\item Position the substrate with W powder into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:seed};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:seed};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.3 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:seed}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} The growth steps are as following:

@@

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:naw};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:naw};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.4 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:naw}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

\begin{enumerate}
\item Prepare 200 -- 300 g Sulfur in a small boat;
\item Vent the chamber to 1 atm, and position the as-grown \ce{WO3} sample and small boat with S into chamber as indicated in Fig.~\ref{fig:suf};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Add liquid nitrogen into cold trap; 
\item Admit gases (30 sccm Ar) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:suf}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} The growth steps are as following:

@@

\begin{enumerate}
\item Load $\sim$1 g Mo powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:namo};
\item Vent the chamber to 1 atm (32-33 Torr reading on gauge), load the long boat with the substrate and source as shown in Fig.~\ref{fig:namo};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 10 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:namo}; 
\item Close the butterfly valve to pressure gauge (V-6 in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

Change heating procedure ( heating time and temperature) by the following steps:
\begin{enumerate}
\item hold $\Omega$ key for 3 second; a new display should show up, 
\item use $Xi$ key to circle until ``r.s'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

\subsection{sulfurization}

@@

\subsection{TEM-Raman integrated measurements}

\subsection{data processing}

\textbf{Multipeaks fitting}

\textbf{3D pdf}

>>>>

\date{\today}
Prepared by Tao Sheng

\begin{landscape}
\begin{figure}[htb]
\centering
\includegraphics[width=8in]{CVD_model.jpg}
\caption{Sketch of CVD system for oxide growth, where A1: quartz tube; B1: bubbler; C1-2: gas cylinders; E1: mechanical pump; H1-2: ceramic heater; MFC: flow controller; P1: pressure gauge; V1-4: valves; V5-7: butterfly valves. Note: the thermal sensor attached on H-1 is not shown. }
\label{fig:ch2cvd}
\end{figure}
\end{landscape}

A schematic diagram of the home-built CVD system is shown in Fig.~\ref{fig:ch2cvd}. 
The following text will refer to this diagram using \fbox{symbol in box} when a specific component is mentioned. Please note that the actual CVD system is subject to changes, \emph{e.g.}, in the sulfurization CVD, a cold trap is used and oxygen tank is absent; whereas in the ZnTe CVD, a pressure controller is added and hydrogen instead of oxygen is used.

In this instruction, a few ``unusual'' units will be used frequently, i.e., Torr for pressure and sccm for flow rate. Note 1 atm $\equiv$ 760 Torr, and 1 sccm means 1 cubic centimeter per minute at standard condition (RT, 1 atm).

To visualize the important components in the CVD system, a photograph gallery is presented in Fig.~\ref{fig:gallery}. Check to make sure you can recognize it in both the schematic drawing (Fig.~\ref{fig:ch2cvd}) and the actual system.

\begin{figure}[htb]
\centering
\subfloat[\fbox{P-1}]{\label{fig:gauge}\includegraphics[width=0.4\textwidth]{pressure_gauge}}\hspace{0.04\textwidth}
\subfloat[]{\label{fig:switch}\includegraphics[width=0.4\textwidth]{toggle_switch}}

\caption{Photograph of pressure gauge reading panel}
\label{fig:gallery}
\end{figure}

Before performing growth, check the CVD system to confirm its normal state, where the vacuum in idle status is manifested as:
\begin{itemize}
\item 5-7 mTorr reading for the pressure gauge (\fbox{P-1})of ZnTe CVD;
\item 20-22 mTorr reading for the pressure gauge (\fbox{P-1})of oxide CVD, as shown in Fig.~\ref{fig:gauge};
\item 45-50 mTorr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD. 
\end{itemize} 
and the mass flow controller reading (\fbox{MFC}) should be either negative or zero.

\textcolor{red}{If large deviation occurs, check the vacuum sealing and report to lab manager.}

When the chamber is purged with Ar, the indications of actual inner pressure reaching 1 atm inside are shown as: 
\begin{itemize}
\item 760 Torr reading for the pressure gauge (\fbox{P-1}) of ZnTe CVD;
\item 32-33 Torr reading for the pressure gauge (\fbox{P-1})of oxide CVD;
\item 24 Torr reading for the pressure gauge (\fbox{P-1}) of sulfur CVD.  
\end{itemize}

\textcolor{red}{\textbf{Avoid} using higher venting pressure, otherwise it might damage the chamber.}

\section{Basic Operation}
Some common operations used in all CVD system are listed. 
\subsection{Venting the chamber}
The Ar gas switch panel is shown in Fig.~\ref{fig:switch}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{toggle_switch.jpg}
\caption{Photograph of toggle switch panel}
\label{fig:switch}
\end{figure}
To load/unload sample into/out of the chamber, one first needs to bring the pressure up to 1 atm. This is done by purging the chamber using Ar gas using steps as following (\textbf{FOLLOW THE EXACT ORDER}):
\begin{enumerate}
\item close \fbox{V-5}, you should observe \fbox{P-1} reading increases;
\item toggle Ar gas switch from OFF to ON, wait for 10 s to see the corresponding \fbox{MFC} display setting flow rate;
\item toggle Ar gas purge switch, watching pressure gauge \fbox{P-1} closely; 
\item Turn off Ar purge switch rapidly when ``1 atm'' is reached; 
\item Slowly open \fbox{V-4} to test the ``water'' level in \fbox{B-1}. Close \fbox{V-4} if the level goes up; fully open \fbox{V-4} if otherwise. 
\end{enumerate}
%Using the same procedure when harvesting the samples.

@@

\subsection{Using Mass Flow Controller}

\subsection{Starting and Stop Heating} 
The heating is controlled by a close-loop PID method, with the control panel shown in Fig.~\ref{fig:omega}. 
\begin{figure}[htb]
\centering
\includegraphics[width=0.3\textwidth]{transformer}
\includegraphics[width=0.3\textwidth]{omega_temp}

\includegraphics[width=0.3\textwidth]{temp_cont2}
\includegraphics[width=0.3\textwidth]{temp_cont3}
\caption{Front panel of temperature controller, and the four keys are denoted as $\Omega$, $\nabla$, $\Delta$, and $\Xi$ here. SV means setting value; PV means present value.}
\label{fig:omega}
\end{figure}

Change CVD from standby to heating mode by the following steps:
\begin{enumerate}
\item turn on the voltage transformer; 
\item hold $\Xi$ key for 3 second;
\item use $\nabla$ or $\Delta$ key to circle until ``r.s'' emerges;
\item hold $\Xi$ key for 1 second to confirm.
\end{enumerate}

@@

\section{Advanced Operations and Emergence Procedures}

@@

\section{Substrate Preparation}

@@

The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The treatment method in the seeded growth only includes usual cleaning using organic solvents. The growth steps are as following:

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;  
\item Load a thin layer of 3N W powder on the clean substrate, spread them uniformly by putting the polished side of another clean Si substrate against the power and sliding the top substrate gently; 
\item Position the substrate with W powder into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:seed};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:seed};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.3 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:seed}; 
\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} The growth steps are as following:

@@

\begin{enumerate}
\item Load $\sim$1 g high purity W powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:naw};
\item Vent the chamber to 1 atm, load the long boat with the substrate and source as shown in Fig.~\ref{fig:naw};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 0.4 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:naw}; 
\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

\begin{enumerate}
\item Prepare 200 -- 300 mg Sulfur in a small boat;
\item Vent the chamber to 1 atm, and position the as-grown \ce{WO3} sample and small boat with S into chamber as indicated in Fig.~\ref{fig:suf};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Add liquid nitrogen into cold trap; 
\item Admit gases (30 sccm Ar) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:suf}; 
\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

The substrate used here can be either Si or 1$\mu$m \ce{SiO2}-Si. The substrate treatment in this growth includes \begin{enumerate*}[label=\itshape\alph*\upshape)]
\item usual cleaning using organic solvents;
\item plasma cleaning (2 Torr oxygen, 3 min); and
\item drop casting of NaOH solution (50 $\mu$L, 0.01 mol/L).
\end{enumerate*} When other alkaline ions containing substrates are used, such as glass, ITO glass and mica, the NaOH treatment is skipped. The growth steps are as following:

@@

\begin{enumerate}
\item Load $\sim$1 g Mo powder into the handler end of the long boat, spread the power evenly into 1 in long;
\item Position the NaOH--treated substrate into the same long boat in a way that when the whole boat in loaded into the chamber, the separation between substrate and power source is the same as indicated in Fig.~\ref{fig:namo};
\item Vent the chamber to 1 atm (32-33 Torr reading on gauge), load the long boat with the substrate and source as shown in Fig.~\ref{fig:namo};
\item Seal the chamber, check the valve status, pump down and record the pressure gauge reading when it becomes stabilized; 
\item Admit gases (10 sccm Ar and 10 sccm \ce{O2}) into the chamber, record the corresponding pressure reading;
\item Close the furnace, begin the heating procedure as required in Fig.~\ref{fig:namo}; 
\item Close the butterfly valve to pressure gauge (\fbox{V-6} in Fig.~\ref{fig:ch2cvd});
\item Put up the warning sign beside the furnace;
\end{enumerate}

@@

@@
